Title

### 2024-05-07 paper/main.tex
Updates

% Packages added by me.
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}

@@

@@

\textbf{Para 5: Contributions}
\begin{enumerate}
	\item An effect size measure for mixed data. 
	\item A web-based tool to help with both model testing and construction. Combining both domain knowledge and data.
\end{enumerate}

@@

\section{Background}
We consider one-dimensional variables $ X $, and $ Y $ and a possibly
multi-dimensional co$ Z = Z_1, \cdots, Z_k $, potentially being an empty set $
Z = \emptyset $. We consider various scenarios where the variables $ X $, $ Y $
and $ Z $ could be either discrete, ordinal, or continuous. With mixed data, we
mean an arbitrary mix of variable types among $ X $, $ Y $, and $ Z $.

@@

\subsection{Effect Size Measures}

\subsubsection{$ X $ and $ Y $ are continuous}
In the case when $ \bm{Z} = \emptyset $, and when both $ X $ and $ Y $ are
continuous variables, Pearson's correlation coefficient based test can be used
which also gives an effect size measure. The p-value computation requires the
data to be normally distributed but other statistics can be used such as
Spearman's rank correlation, or Kendall's Tau.

@@

\subsubsection{All $ X $, $ Y $, $ Z $ are discrete}

@@

\subsubsection{$ X $ is ordinal and $ Y $ is continuous}
Polyserial Correlation

@@

\subsubsection{$ X $ and $ Y $ are ordinal}
Polychoric Correlation

\subsubsection{Mixed data}
Recently multiple tests for mixed data have been proposed but they do not have
an effect size measure. We propose one based on canonical correlations.

\subsection{Canonical Correlations}
Canonical correlations are generalization of correlations to multi-dimensional case.

Multiple effect sizes measures based on canonical correations are available.

\section{Effect size for mixed data}
In this section, we use canonical correlations to define an effect size for mixed data CI tests. The main idea is to transform any CI test into j
We consider the following two cases separately:

\subsection{No conditional variables}
When we have no conditonal variables, we are trying

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[scale=0.25]{../../presentations/2024_05_das/1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[scale=0.25]{../../presentations/2024_05_das/2.png}
	\end{subfigure}
	\caption{\todo[inline]{Insert screenshots of the web-tool}}
\end{figure}

\section{Empirical Analysis}
To compare how well does creating a graph manually based on effect sizes and
p-value compare to algorithmic approaches, we performed some emperical
analysis.

@@

\todo[inline]{Summarize this section and equaiton in an algorithm}
\todo[inline]{Show a consistency proof for this expert simulation}

@@

>>>>

% Packages added by me.
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
\usepackage[ruled]{algorithm2e}

@@

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}

@@

\textbf{Para 5: Contributions}
\begin{enumerate}
	\item We present an effect size measure based on canonical correlations
		for mixed data that generalizes some of the commonly used
		effect size in special cases such as partial correlation
		coefficient for continuous variables, and Cram\'er's V for
		discrete variables.
	\item We also developed a web-based tool to help researches in
		constructing and testing and modifying their DAGs using CI tests and
		effect size measures.
\end{enumerate}

@@

\section{Background}
We represent uni-dimensional variables as $ X $ and multi-dimensional variables
as $ \bm{Z} $. We consider the case of estimating association between $ X $,
and $ Y $ is the presence of a set of conditioning variables $ \bm{Z} = Z_1,
\cdots, Z_k $, potentially being an empty set $ \bm{Z} = \emptyset $. We use $
\rvert \bm{Z} \rvert $ to denote the cardinality of the variable $ \bm{Z} $. We
consider various scenarios where the variables $ X $, $ Y $ and $ \bm{Z} $
could be either discrete, ordinal, or continuous. With mixed data, we mean an
arbitrary mix of variable types among $ X $, $ Y $, and $ \bm{Z} $.

@@

\subsection{Effect size Measures}
In this section, we give a background on some of the commonly used effect size
measures in the context of CI testing.

\paragraph{$ X $ and $ Y $ are continuous}
In the case when $ \bm{Z} = \emptyset $, and when both $ X $ and $ Y $ are
continuous variables, Pearson's correlation coefficient based test can be used
which also gives an effect size measure. The p-value computation requires the
data to be normally distributed but other statistics can be used such as
Spearman's rank correlation, or Kendall's Tau.

@@

\paragraph{All variables are discrete}

@@

\paragraph{$ X $ is ordinal and $ Y $ is continuous}
Polyserial Correlation

@@

\paragraph{$ X $ and $ Y $ are ordinal}
Polychoric Correlation

\paragraph{Mixed data}
Recently multiple tests for mixed data have been proposed but they do not have
an effect size measure. We propose one based on canonical correlations.

\subsection{Canonical Correlation}
Canonical correlations are generalization of correlations to multi-dimensional variables.

\begin{definition}
	Given two sets of random variables $ \bm{U} = (U_1, U_2, \cdots, U_p) $
	and $ \bm{V} = (V_1, V_2, \cdots, V_q) $, canonical correlation between
	them, $\rho(\bm{U}, \bm{V}) $ is defined as:

	\begin{equation}
		\rho(\bm{U}, \bm{V}) = \sup_{a, b} \frac{a^T \Sigma_{\bm{U}\bm{V}} b}{\sqrt{a^T \Sigma_{\bm{U}\bm{U}} a} \sqrt{b^T \Sigma_{\bm{V}\bm{V}} b}}
	\end{equation}

\end{definition}

	Canonical correlations try to find linear transformations $ a $ and $ b
	$ of $ \bm{U} $ and $ \bm{V} $ such that the correlations between the
	columns of $ a^T \bm{U} $ and $ b^T \bm{V} $ is maximized. The
	individual columns of $ a^T \bm{U} $ and $ b^T \bm{V} $ are
	independent. In the case when $ \rvert U \rvert = \rvert V \rvert = 1$,
	canonical correlations are equivalent to Pearson's correlation
	coefficient.

Multiple effect sizes measures based on canonical correlation are available.
\begin{itemize}
	\item Wilks' Lambda: $ \Lambda = \prod (1 - \phi_i^2) $
	\item Roy's Largest Root: $ \theta = \phi_{\max}^2 $
	\item Pillai's Trace: $ \tau = \sum \phi_i^2 $
\end{itemize}
We use Pillai's Trace in this paper. \todo[inline]{Why?}.

\section{Effect size for mixed data}
In this section, we use canonical correlations to define an effect size measure
for mixed data CI tests. Our approach is similar to the approach used for the
continuous variable case.

\subsection{No conditional variables}
When we have no conditonal variables, we need to convert the variables into

@@

% \begin{figure}
% 	\centering
% 	\begin{subfigure}{0.5\textwidth}
% 		\includegraphics[scale=0.25]{../../presentations/2024_05_das/2.png}
% 	\end{subfigure}%
% 	\begin{subfigure}{0.5\textwidth}
% 		\includegraphics[scale=0.25]{../../presentations/2024_05_das/5.png}
% 	\end{subfigure}
% 	\caption{Screenshots of the web-tool. \todo[inline]{Insert screenshots of the web-tool}}
% \end{figure}

\section{Empirical Analysis}
To compare how well does creating a graph manually based on effect sizes and
p-value compare to algorithmic approaches, we performed some empirical
analysis.

@@

\todo[inline]{Summarize this section and equation in an algorithm}
\todo[inline]{Show a consistency proof for this expert simulation}

@@

\begin{algorithm}
	\caption{Expert Simulation}
	\While{True}{
	   $ e \gets \textnormal{Effects}(G) > \textnormal{THRESHOLD} $ \;
	   \If{$ \textnormal{len}(e) $}{
		   $ \textnormal{return}(G) $ \;
	   }
	   $ X, Y \gets \max_{X, Y} e $\;
	   $ dir \gets Expert(X, Y) $ \;
	}

\end{algorithm}
